A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-17 tex/body.tex
cleaner handling of memoriam
more

\noindent\hfill\emph{In memoriam Morgan Deters 1979--2015}

@@

@@

\paragraph{Related Work.}
Although it was written several years ago,
Barrett et al.\ \cite{barrett-et-al-2007} still provides a good account of
related work. Since then, datatypes have been added to the SMT solver
Z3 in unpublished work by Leonardo de Moura and to a SPASS-like prototypical
superposition prover called Pirate by Daniel Wand.
Closely related is the automatic structural
induction in CVC4 by Reynolds and Kuncak \cite{reynolds-kuncak-2015} and in
the SPASS-like prototype by Wand and Weidenbach \cite{wand-weidenbach-201x};
both methods naturally depend on a notion of datatype.
% \textbf{TODO:} http://frocos2013.loria.fr/slides/Peltier.pdf
% \textbf{TODO:} Others (or at least add "e.g.")
% \textbf{TODO:} Nitpick

%\textbf{TODO}:
%  * mu-calculus
%  * Klop et al. (streams) Andrew Lice % http://joerg.endrullis.de/
%  * Ro\c{s}u --- equality of streams is...
%     http://dl.acm.org/citation.cfm?doid=1159803.1159827

>>>>

\begin{nomemoriam}
%%% TODO: Unphantom
\noindent\hfill\emph{\phantom{In memoriam Morgan Deters 1979--2015}}

\vspace*{-6\smallskipamount}
\end{nomemoriam}
\begin{memoriam}
\noindent\hfill\emph{\relax{In memoriam Morgan Deters 1979--2015}}
\end{memoriam}

@@

\begin{nomemoriam}
%%% TODO: Unphantom
\vskip3\smallskipamount
\end{nomemoriam}

@@

\paragraph{Related Work.}
Although it was written several years ago,
Barrett et al.\ \cite{barrett-et-al-2007} still provides a good account of
related work. Since then, datatypes have been added to the SMT solver
Z3 in unpublished work by Leonardo de Moura and to a SPASS-like prototypical
superposition prover called Pirate by Daniel Wand.
Closely related is the automatic structural
induction in superposition-based provers \cite{kersani-peltier-2013,wand-weidenbach-201x}
and SMT solvers \cite{reynolds-kuncak-2015}.
%
Datatypes are explicitly supported by the higher-order model finder Refute
\cite{weber-2008}. Its successor, Nitpick \cite{blanchette-nipkow-2010}, can
also find models involving cyclic codatatype values. The $\mu$-notation is
inspired by the $\mu$-calculus \cite[etc.]{kozen-1983,endrullis-et-al-2011}.

% \textbf{TODO:} Nitpick

%\textbf{TODO}:
%  * Klop et al. (streams) Andrew Lice % http://joerg.endrullis.de/
%  * Ro\c{s}u --- equality of streams is...
%     http://dl.acm.org/citation.cfm?doid=1159803.1159827
